\documentclass[a4paper,12pt]{report}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{textcomp}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PDF INFO 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
	pdfauthor   = {Erwan Douaille},
	pdftitle    = {Resume},
	pdfsubject  = {Resume},
	pdfkeywords = {Resume},
	pdfcreator  = {PDFLaTeX},
	pdfproducer = {PDFLaTeX}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\frenchbsetup{StandardLists=true}
\newcommand{\marge}{18mm}
\usepackage[left=\marge,right=\marge,top=\marge,bottom=\marge]{geometry}
\pagestyle{fancy}
\setlength{\headheight}{14pt}
\chead{
  \textbf{Nom :} Douaille
  \hspace{2em}
  \textbf{Prénom :} Erwan
  \hspace{2em}
  \textbf{Groupe :} M1 Info groupe 1}
\renewcommand{\headrulewidth}{0pt}
\linespread{1.3}
\setlength{\columnseprule}{0.2pt}

\author{Douaille Erwan}
\title{}
\titleformat{\chapter}[hang]{\bf\huge}{\thechapter}{2pc}{}

\begin{document}

\section*{Resume: Iceland looks to serve the world}

The text is about why Iceland looks the best country for a server farm.\\

Power consumption keeping cooling server farms is more than a half of the electricity consumption of data-center. The main goal of industrials is how to save money and how to fix the problem of server cooling. Data center industries also reach an unacceptable carbon footprint. Comparable as the airline industry. Data center industry have to become grow due to the cloud computing evolution, which it means than a solution to fix cooling and consumption problem have to be found. 

Fresh weather and environment friendly energy are the solutions, Iceland provides both of them. The Iceland temperature is close to 0 degrees the whole year and geothermal power is renewable and carbon free. This solution has been approved by 

This natural gift looks really good for the future of the Iceland economy, since the 2007 crash everything goes wrong.

Since the Iceland solution has been found many industrials decided to move in. But many industry like banks didn't approved this solution due to security problem and possible latency. Stock Exchange is needed fast internet connection. Iceland is connected to the world with optical fibre. The actual latency between Iceland and London is actually 17 milliseconds which is really quite good and efficient at least for 70 \% of the internal data exchange


\end{document}